Solid State Assignment Two

### 2016-04-15 solid_state/latex/a2.tex
a2.tex

>>>>

\section{Problem Four: Heteronuclear Diatomic Molecule}
Here we follow the same process for finding the energies of a multiatomic system that we used
in problem Two: defining which atomic wave functions overlap on-site and off-site, deciding
the energies of these overlaps, creating a Hamiltonian and finding the energies of the
Hamiltonian. We are given that for this heteroatomic system atom A's on-site interaction
energy is $E_A$ and B's is $E_B$. Similarly B's is $E_B$, and $E_A > E_B$. We then let out
hopping integral take the value $H_{12} = H_{21} = \beta$. Thus our Hamiltonian is:

\begin{align*}
  H &=
  \begin{pmatrix}
    E_A & \beta\\
    \beta & E_B\\
  \end{pmatrix}
\end{align*}

Our next job is to find the eigenvalues of this matrix:

\begin{align*}
  \det\begin{pmatrix}
    E_A-\lambda & \beta\\
    \beta & E_B-\lambda\\
  \end{pmatrix}
  &= 0\\
  (E_A-\lambda)(E_B-\lambda) - \beta^2 &= 0\\
  \lambda^2 - \lambda(E_A + E_B )+ E_AE_B - \beta^2 &= 0\\
  \lambda &= \frac{(E_A + E_B) \pm \sqrt{(E_A + E_B)^2 - 4(E_AE_B - \beta^2)}}{2}\\
  &= \frac{(E_A + E_B) \pm \sqrt{E_A^2 + E_B^2 - 2E_AE_B + 4\beta^2}}{2}\\
  &= \frac{(E_A + E_B) \pm \sqrt{(E_A - E_B)^2 + 4\beta^2}}{2}\\
  &= \frac{(E_A + E_B)}{2} \pm \sqrt{\frac{(E_A - E_B)^2}{4} + \beta^2}\\
\end{align*}
